\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-18 draft.tex
add bookmarks for appendix and references
fix subsection labels
add sentence on multiple equilibria at top of sec:res

\addtolength{\textwidth}{1.3in}
\addtolength{\oddsidemargin}{-.65in} %left margin
\addtolength{\evensidemargin}{-.65in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-.5in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.375in}
\renewcommand{\baselinestretch}{1.0}
\renewcommand{\thesection}{\Roman{section}} 
\renewcommand{\thesubsection}{\thesection.\Roman{subsection}}
\linespread{1.5}

@@

Although uncertainty is present in the environment under consideration here, information about that uncertainty is symmetric. Therefore the appropriate equilibrium notion is subgame perfect Nash equilibrium.

@@

\section*{Appendix}
\label{sec:app}
\noindent \textbf{\hypertarget{Pr_2NNB}{Proof of Proposition~\ref{prop:2NNB}}}: \\
Without loss of generality, assume that it is the legislators at $-\frac{1}{2}$ and $0$ that are bribed. The first order conditions with respect to the bribes for these two legislators are
	\begin{equation}
		\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
	\end{equation}
	and
	\begin{equation}
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
		\label{eq:base}
	\end{equation}

@@

\newpage
\section*{References}

>>>>

\addtolength{\textwidth}{1.3in}
\addtolength{\oddsidemargin}{-.65in} %left margin
\addtolength{\evensidemargin}{-.65in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-.5in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.375in}
\renewcommand{\baselinestretch}{1.0}
\renewcommand{\thesection}{\Roman{section}} 
\renewcommand{\thesubsection}{\thesection.\Alph{subsection}}
\linespread{1.5}

@@

Although uncertainty is present in the environment under consideration here, information about that uncertainty is symmetric. Therefore the the solution concept employed here is subgame perfect Nash equilibrium.

Whenever there is a possibility of multiple equilibria, I will focus on the one that maximizes the welfare of Vote Buyer A, the first mover.

@@

\section*{Appendix}
\label{sec:app}
\pdfbookmark{Appendix}{sec:appendix}
\noindent \textbf{\hypertarget{Pr_2NNB}{Proof of Proposition~\ref{prop:2NNB}}}: \\
Without loss of generality, assume that it is the legislators at $-\frac{1}{2}$ and $0$ that are bribed. The first order conditions with respect to the bribes for these two legislators are
	\begin{equation}
		\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
	\end{equation}
	and
	\begin{equation}
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
		\label{eq:base}
	\end{equation}

@@

\newpage
\section*{References}
\pdfbookmark{References}{sec:refs}
